---
output: html_document
editor_options: 
  chunk_output_type: console
---
Lesson 3
========================================================

***

### What to Do First?
Notes:
???????????????????????????????????????.
***

### Pseudo-Facebook User Data
Notes:
????????????, ???????????????????????????
```{r Pseudo-Facebook User Data}
getwd()
list.dirs()
setwd('~/Documents/GitHub/data-analyst/projects_zh/P4 explore_data/')
pf <- read.delim('pseudo_facebook.tsv')
names(pf)
```

***

### Histogram of Users' Birthdays
Notes:
????????????????????????, ???????????????, ???????????????
```{r Histogram of Users\' Birthdays}
library(ggplot2)
qplot(data = pf, x = pf$dob_day)
```

***

#### What are some things that you notice about this histogram?
Response:The first month is too high.

***

### Moira's Investigation
Notes: ?????????????????????

***

### Estimating Your Audience Size
Notes: ??????????????????

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response: ????????????????????????

#### How many of your friends do you think saw that post?
Response: ?????????

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response: 80%

***

### Perceived Audience Size
Notes: 2

***
### Faceting
Notes: 

```{r Faceting}
ggplot(data = pf, aes(x = dob_day)) +
  geom_histogram(binwidth = 1) +
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~dob_month, ncol = 3)
```

#### Let???s take another look at our plot. What stands out to you here?
Response:????????????????????????

***

### Be Skeptical - Outliers and Anomalies
Notes:?????????????????????????????????????????????, ??????????????????????????????????????????????????????.

***

### Moira's Outlier
Notes: ????????????????????????, ???????????????????????????????????????????????????
#### Which case do you think applies to Moira???s outlier?
Response: 

***

### Friend Count
Notes:??????

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x = pf$friend_count, data = pf)
```

#### How is this plot similar to Moira's first plot?
Response:?????????plot?????????, ??????????????????????????????????????????.

***

### Limiting the Axes
Notes:?????????????????????????????????, ????????????????????????????????????.

```{r Limiting the Axes}
# ?????????
qplot(x = pf$friend_count, data = pf) + scale_x_continuous(limits = c(0, 500))
# ?????????
qplot(x = friend_count, data = pf, xlim = c(0, 50))
```

### Exploring with Bin Width
Notes: ????????????????????????????????????????????????, ???????????????????????????????????????, ???????????????????????????????????????????????????.
???????????????, ????????????????????????????????????.
***

### Adjusting the Bin Width
Notes: ??????friend count?????????, ???25?????????, ??????????????????????????????, binwidth???????????????????????????.

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_grid(. ~ gender)
```

***

### Omitting NA Values
Notes: ???????????????????????????na??????, ????????????subset????????????, ????????????na.omit??????.

```{r Omitting NA Values}
qplot(x = friend_count, data = na.omit(pf),binwidth = 10)+
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_grid(. ~ gender)

qplot(friend_count, data = subset(pf, !is.na(pf$gender))) +
  facet_grid(gender ~ .)
```

***

### Statistics 'by' Gender
Notes: ??????by????????????????????????

```{r Statistics \'by\' Gender}
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response: women

#### What's the difference between the median friend count for women and men?
Response: 22

#### Why would the median be a better measure than the mean?
Response: ??????, ??????????????????????????????????????????.

***

### Tenure
Notes: ??????Facebook?????????

```{r Tenure}
qplot(x = pf$tenure, data = pf, binwidth = 0.25,
      colour = I('black'), fill = I('#099DD9'),
      xlab = 'Facebook time spending') +
  scale_x_continuous(limits = c(0, 7), breaks = seq(0, 7, 1))
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(pf$tenure/365, data = pf, binwidth = 0.25,
      colour = I('black'), fill = I('red'),
      xlab = 'year spend in facebook') +
  scale_x_continuous(limits = c(0, 7), breaks = seq(0, 7, 1))
```

***

### Labeling Plots
Notes: ??????label

```{r Labeling Plots}
qplot(pf$tenure, data = pf, xlab = 'x label')
```

***

### User Ages
Notes: 

```{r User Ages}
qplot(pf$age, data = pf, binwidth = 1) +
  scale_x_continuous(limits = c(13, 80), breaks = seq(13, 133, 1))
```

#### What do you notice?
Response: ????????????????????????.

***

### The Spread of Memes
Notes: ??????????????????????????????, ??????????????????????????????????????????????????????????????????.

***

### Lada's Money Bag Meme
Notes: ??????????????????????????????.

***

### Transforming Data
Notes: 
```{r Transforming Data}
p1 <- qplot(pf$friend_count, data = pf, xlab = 'normal')
p2 <- qplot(pf$friend_count + 1, data = pf, xlab = 'log10') + 
  scale_x_log10()
p3 <- qplot(pf$friend_count, data = pf, xlab = "sqrt") +
  scale_x_sqrt()
grid.arrange(p1, p2, p3, ncol=2)
```


***

### Add a Scaling Layer
Notes: ????????????????????????

```{r Add a Scaling Layer}
p1 <- qplot(pf$friend_count, data = pf, xlab = 'normal')
p2 <- qplot(pf$friend_count + 1, data = pf, xlab = 'log10') + 
  scale_x_log10()
p3 <- qplot(pf$friend_count, data = pf, xlab = "sqrt") +
  scale_x_sqrt()
grid.arrange(p1, p2, p3, ncol=2)
```

***


### Frequency Polygons
??????????????????????????????????????????????????????
```{r Frequency Polygons}
ggplot(aes(x = www_likes) ,data = subset(pf, !is.na(pf$gender))) +
  geom_freqpoly(aes(color = gender))
# the x aixs can't be the original one, because the shape is not consistent.
ggplot(aes(x = www_likes), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender)) +
  scale_x_continuous() +
  scale_x_log10()
# ????????????????????????, ??????????????????????????????????????????.

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(pf$www_likes, pf$gender, sum)
```


***

### Box Plots
Notes: ???????????????

```{r Box Plots}
qplot(gender, friend_count, data = subset(pf, !is.na(gender) & friend_count < 1000), geom = "boxplot")
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(gender, friend_count, data = subset(pf, !is.na(gender)), geom = "boxplot", ylim = c(0, 1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
qplot(gender, friend_count, data = subset(pf, !is.na(gender)), geom = "boxplot") +
  coord_cartesian(ylim = c(0, 250))

by(pf$friend_count, pf$gender, summary)
```

#### On average, who initiated more friendships in our sample: men or women?
Response: women
#### Write about some ways that you can verify your answer.
Response: ??????initiated ?????????
```{r Friend Requests by Gender}
qplot(gender, friendships_initiated, data = subset(pf, !is.na(gender)), geom = "boxplot") +
  coord_cartesian(ylim = c(0, 150))
```

Response:

***

### Getting Logical
Notes: 

```{r Getting Logical}
pf$mobile_check_in <- NA
pf$mobile_check_in <- (ifelse(pf$mobile_likes > 0, 1, 0))
pf$mobile_check_in <- factor(pf$mobile_check_in)
table(pf$mobile_check_in)
sum(pf$mobile_check_in == 1) / length(pf$mobile_check_in)
```

Response:
64%
***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!