---
output: html_document
editor_options: 
  chunk_output_type: console
---
TITLE by HOUBOWEI
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(grid)
library(gridExtra)
library(readxl)
library(tidyr)
library(dplyr)
library(lubridate)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
population <- read_excel(path = "indicator gapminder population.xlsx",col_names = TRUE)
```

# wrangle data
```{r echo=FALSE, Univariate_Plots}
population_clean <- population %>% gather("year", "populatin", -1)
```
```{r}
head(population_clean)
```
```{r}
# change year datatype into date type.
strsplit(x = population_clean$year, ".", fixed = TRUE)[[1]][[1]]
```
# 
```{r}
population_clean$year <- population_clean$year %>% as.numeric()
```

```{r}
population_clean %>% head()
```
```{r}
summary(population_clean)
```

```{r}
# group by year
p1 <- population_clean %>% subset(!is.na(populatin)) %>%  group_by(year) %>% summarise(sum = sum(populatin))
qplot(x=year,y=sum,data=p1)
```
# facebook birthday
```{r}
birthdaysExample <- read.csv("eda-course-materials/lesson3/birthdaysExample.csv")
birthdaysExample$dates <-as.Date(birthdaysExample$dates,format = "%m/%d/%y")
```

```{r}
birthdaysExample <- birthdaysExample %>% separate(dates, c("year", "month", "day"), "-")
```

```{r}
month_count <- birthdaysExample %>% filter(!is.na(month)) %>% group_by(month) %>% summarise(n =n()) 
```

```{r}
qplot(x = n,data = month_count)
```

```{r}
qplot(x=month, data = birthdaysExample)
```
March has most people.
```{r}
qplot(day, data = birthdaysExample)
birthdaysExample_clean <- birthdaysExample %>% separate(date, c("year", "month", "day"), sep = "-")
birthdaysExample_clean %>% group_by(month) %>% summarise(n())
```
14 is the most day.
```{r}
names(birthdaysExample)
```

```{r}
birthdaysExample
birthdaysExample <- unite(birthdaysExample, "date", c(year, month, day), sep = "-")
qplot(x =date, data =birthdaysExample)
```

```{r}
names(birthdaysExample)
birthdaysExample %>% group_by(date) %>% summarise(n = n()) %>% arrange(desc(n))
```
```{r}
birthdaysExample %>% summarise(n())
```
```{r}
birthdaysExample %>% group_by(date) %>% summarise(n()) %>% summary()
```

# Lesson 5 
Continue digging out the data of population and use the techniques in lesson 5.
```{r summary data}
population_clean %>% summary()
```
## Change the name of Total to city
```{r}
population_clean <- population_clean %>% rename("population" = 'populatin')
```
## Group population by city
```{r}
population_group_by_city <- population_clean %>% 
  group_by(country) %>% 
  summarise(max_population = max(population),
            min_population = min(population),
            mean_population = mean(population),
            median_population = median(population),
            n = n()) %>% 
  arrange(max_population)
population_group_by_city <- 
  population_group_by_city %>% 
  mutate(change = max_population - min_population,
         change_by_percent = change / min_population) %>% 
  arrange(desc(change))
population_group_by_city %>% head()
population_group_by_city %>% arrange(desc(change_by_percent))
```
1. The most big change in population is happend in India and China.
2. The most big change compared to history is Hong Kong, China, which is 363 times bigger than before.
### Max versus Population 
```{r india's population changes by year}
p1 <- ggplot(aes(year, population/1e+8), data = subset(population_clean, country == 'India'))+
  geom_point()+
  ylab("India")+
  geom_smooth()

```
```{r Hong Kong's population changes by year}
p2 <- ggplot(aes(year, population/1e+8), data = subset(population_clean, country == 'Hong Kong, China'))+
  ylab("Hong Kong") + 
  geom_point()+
  geom_smooth()
```
```{r China}
p3 <- ggplot(aes(year, population/1e+8), data = subset(population_clean,  country == "China"))+
  ylab("China")+
  geom_point()+
  geom_smooth()
```
```{r combine three images}
grid.arrange(p1, p2, p3)
```
It is obvious that, China and Hong Kong's increasing speed is slower down.
But India is still increasing fast.
